Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex

In contrast to our approach, \citet{immer2021improving} use a subset of the full GP model \todo{isn't the subset on the data points?} to reduce the computational complexity. As a result, this is a less principled approach for building a sparse model since it ignores the dataset's information. It is important to highlight that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using the neural network definition \cref{eq-empirical-risk}. 
More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network. Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP model. \todo{shouldn't this sentence be clear from the context? we derive the mean/kernel function that define the process, then we have a sparse GP already}

\section{Sparse Function-space Sequential Learning}

@@

\subsection{\our for Continual Learning}
% Definition of CL -> a sequence of tasks 
In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training. However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model. \todo{this term is replacing the missing data}

>>>>

In contrast to our approach, \citet{immer2021improving} use a subset of the full GP model \todo{isn't the subset on the data points?} to reduce the computational complexity. As a result, this is a less principled approach for building a sparse model since it ignores the dataset's information. It is important to highlight that the sparsifying process is independent of the approximate inference technique because the dual variables of \cref{eq:dual_param} are computed using \cref{eq-empirical-risk} and a Laplace approximation.
More complicated inference techniques, such as variational inference, could be used, but given its simplicity, in our experiments we used the Laplace-GGN approximation with the trained neural network. Furthermore, our dual variable view of approximate inference means we do not need to retrain a separate sparse GP model. \todo{shouldn't this sentence be clear from the context? we derive the mean/kernel function that define the process, then we have a sparse GP already}
\section{Sparse Function-space Sequential Learning}

@@

\subsection{\our for Continual Learning}
% Definition of CL -> a sequence of tasks 
In the Continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{n_t}$, which after the task is discarded and cannot be accessed in the later stages of the training. However, rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. After each task, we can use our \our to build a compact representation of the neural network and then use that as an additional term to the training loss to regularize the model. Recent success has shown GP-based regularizers perform better than weight space equivalents getting state-of-the-art on typical CL benchmarks \cite{ pan2020continual, rudner2022continual}. The limitation of such approaches is that they must use subset approximations of the posterior, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. A more principled approach would be to sparsify the data into a low-rank approximation to ensure information wasn't lost, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}

An alternative view of the dual variables is that they parameterize approximate likelihoods, as shown in \citep{adam2021dual, khan2017conjugate}. We can rewrite the GP posterior for $q(\vu)$ in terms of the following approximate normal distributions:
\begin{equation}
 q(\vu) \propto \N(0, \MKzz) \prod_{i=1}^n e^{-\frac{\tilde{\beta}_i}{2}(\tilde{y}_i - \va_i^\top \vu)^2 } = \N(0, \MKzz) \, e^{(\bar{\vy} - \vu)^\top \bar{\MSigma}^{-1}(\bar{\vy} - \vu)}  
\end{equation}
The first normals are the approximate likelihoods where $\va_i^\top = \vkzi^\top \MKzz^{-1}$ and $\tilde{y}_i = \hat{\alpha}_i + f_{\vw^*}(\vx_i)\hat{\beta}$,  replacing $\va_i^\top \vu$ with $\vx_i^{\top}\vw$ and we can see the similarity between the sparse GP and a linear model where the kernel matrix determines the prior. To arrive at the MVN Gaussian, we need to rearrange the quadratic terms to match the prior sufficient statistics we present a derivation in [appendix]. Performing conjugate summation of prior and likelihood, we would arrive at the sparse GP posterior at the inducing points. The correlated covariance structure $\MSigma$ and the corresponding $\tilde{\vy}$ are simply a different form of the sparse dual variables,
\begin{equation}
\quad \bar{\MSigma} =  \MKzz \vbeta_\vu^{-1} \MKzz \quad \bar{\vy} = \MKzz \vbeta_{\vu}\valpha_{\vu}.
\end{equation}
Written as above, we can see that the spare dual variables can be interpreted as a sparse MVN representation. We now show how we use this for a regularizer in continual learning with more details in [appendix].
